\section{Risk Analysis}\label{sec:RiskAnalysis}
During the course of this project several factors may have an influence on the productivity and quality of the work conducted. A collect of the most substantial influences is comprised below. The list is sorted according to magnitude of influence from most to least.

\strong{Working Solo}
This is the first larger project which I have taken part of, where I am the sole member. Several small project along the bachelor were conducted, but for large implementation we were always groups of 2 or more people. This has a major impact as interaction with, and feedback from, other people is based on what you introduce to them in terms of information, compared to when they have been following the implementation process from the start and have a deeper insight to the functionality and scope of the project.

Oftentimes, a new perspective on the situation can yield great ingenuity and also spot potential errors quicker. 

\strong{Moving in with girlfriend}
Around the same date as the project started, my partner and I moved in to a new flat together. As this is the first time I have moved in with someone (apart from family) this of course have great consequences. Routines and sleeping patterns are compromised and financial situations must be solved. Eating hours change, free-time activities change, priorities vary; all which seem like small differences, but can deplete your energy without you noticing.

As we both lived on dorms before, many resources were managed beforehand such as electricity, internet and television, where as this has to be managed privately. 

The distance from the apartment to the university is ~24 times further away, which may have a subconscious influence on meeting attendance and importance.

\strong{Working in new environments}
Throughout this project I expect to work with languages within the .Net framework, which I have little experience in. Most courses on DTU use Java as their base language, meaning this is where I naturally have the most experience. 

Recommended by my supervisor the language F\# will most likely be used as part of the project, and this is also a language I have used in the course "02157 - Functional Programming". Though this language will most likely not be the only language used in the project, meaning this will be the first time I will manage a project consisting of multiple programming languages to interact.

Everything regarding user interfaces have been created in Java, meaning some initial investigation will have to be conducted to find a appropriate tools for these languages (or for .Net in general).

\strong{Job}
While studying, I have a part time job which, while being flexible in work hours, will take time and attention throughout the project span.

\strong{Implementation errors/change}
As with any other software development, errors and changes may occur, meaning either something is behaving in a unwanted matter or has to be rewritten/redesigned during the implementation phase.